%%***( Referencias )****************************************************************

%%==================================================================================
\section{Personas}

Las personas que fueron consultada para la elaboración de este proyecto fueron:

\begin{itemize}
    \item El Profesor a cargo de la materia Eugenio Tamura.
    \item Seis estudiantes de la carrera de Biología entre 8vo y 9no semestre de la Pontificia Universidad Javeriana.
\end{itemize}

%%==================================================================================
\section{Proveedores}
\begin{itemize}
    \item \textsc{Amazon, Inc. - Company Profile, Information, Business Description, History, Background Information on Amazon.com, Inc. Reference for Business.} \url{https://www.amazon.com} (accedido el 22 de abril de 2023).
    
    \item B\&H Photo Video Digital Cameras, Photography, Computers.\url{https://www.bhphotovideo.com}(accedido el 22 de abril de 2023).

    \item Target Corporation - Company Profile, Information, Business Description, History, Background Information on Target Corporation. Reference for Business. \url{https://www.target.com/c/electronics/-/N-5xtg6} (accedido el 22 de abril de 2023).

    \item AWS Lake Formation - Build a Secure Data Lake in Days. Amazon Web Services. \url{https://aws.amazon.com/lake-formation/} (accedido el 22 de abril de 2023).

    \item CDW Corporation - Company Profile, Information, Business Description, History, Background Information on CDW Corporation. Reference for Business. \url{https://www.cdw.com} (accedido el 22 de abril de 2023).

    \item Dell Technologies - Company Profile, Information, Business Description, History, Background Information on Dell Technologies. Reference for Business. \url{https://www.dell.com/es-co/lp/homepage} (accedido el 22 de abril de 2023).
\end{itemize}
    
%%==================================================================================
\begin{comment}
    \bibliographystyle{acm}
    \bibliography{sections/bibliography}
\end{comment}
